Centralized Programming for Distributed Control Planes

### 2016-01-26 paper/compilation.tex
typo

@@

In this section we briefly describe our compilation strategy for \sysname. Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies. The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form. Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.

@@

The high-level language presented in Section~\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints. Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

@@

  \caption{Regular Intemediate Language (RIL) syntax (left), and 
           Propane language expansions (right).}
  \label{fig:rir-syntax}
\end{figure*}

>>>>

The front-end language of \sysname is designed to simplify operators' task of describing preferred paths. That simplicity, however, comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases. We handle this challenge by breaking down the compilation task into multiple stages and developing efficient algorithms for each.

@@

%In this section we briefly describe our compilation strategy for \sysname.

Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies. The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form. Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.

@@

The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints. Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

@@

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
\end{figure*}
